% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

%\sethyphenation[variant=american]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Josemar}{{ F. da Cruz}}           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------
\vspace{-0.2cm}
\begin{aside}
%
\vspace{-0.1cm}
\section{contact}
2265 Starlight CT
APT 888
Melbourne, FL 32904
USA
~
\href{tel:+13216144023}{+1 321 614 4023}
~
\href{mailto:faustino.josemar@gmail.com}{{faustino.josemar
@gmail.com}}
%
\section{programming}
{\color{red} $\varheartsuit$}
Python - expert
Java - proficient
JavaScript - proficient
R - prev experience
PHP - prev experience
C++ - prev experience
%
%
\section{platforms}
\href{https://github.com/josemarfdc}{{\huge \faGithub}{ josemarfdc}}
\href{https://www.linkedin.com/in/josemarfdc}{{\huge \faLinkedin}{ josemarfdc}}
\href{https://twitter.com/josemarfdc}{{\huge \faTwitter}{ josemarfdc}}
\section{languages}
English - fluency
Portuguese - native
Spanish - intermediate
%
\section{interests}
\vspace{0.5cm}
\textbf{professional}
Data Science
Software Development
Machine Learning
\vspace{0.5cm}
\textbf{personal}
debate club
running
cooking
%
\end{aside}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--2019}
{Ph.D. {\normalfont in Computer Science [3.63]}}
{Florida Institute of Technology}
{(Emphasis in Data Science and Complex Social Systems)}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2009--2013}
{B.Sc. {\normalfont in Information Systems [3.40]}}
{Lutheran University of Brazil}
{\vspace{-0.4cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2018--Now}
  {Dept. of Civil Eng. - Florida Institute of Technology}
  {Melbourne FL, USA}
  {\jobtitle{Research Assistant - Data Analytics}\\
  Data processing pipeline, Spatial Data, Natural disaster modelling, \textit{Python Data Science ecossystem, Jupyter Notebooks, Matlab}\\
    Achievements:
  \begin{itemize}
    \item Designed a spatial algorithm that achieved a 90\% matching rate of insurance claim records to property appraiser data.
    \item Implemented data augmentation pipeline using public APIs achieving a 95\% curation accuracy.
  \end{itemize}}
%------------------------------------------------
\entry
  {2017--2018}
  {Academic Support Center - Florida Institute of Technology}
  {Melbourne FL, USA}
  {\jobtitle{Programming Technician}\\
  Web-development, PHP, JavaScript, HTML5, Bootstrap.\\
  Achievement:
  \begin{itemize}
    \item Automated reports of weekly performance of the department reducing time spent by the management on report design to zero.
  \end{itemize}}
%------------------------------------------------
\entry
  {2013--2013}
  {Embraer Executive Jets}
  {Melbourne FL, USA}
  {\jobtitle{Web Reports Designer Intern}\\
  Data pipelining, web-development, Java-web, JavaScript,  Oracle.\\
  Achievement:
  \begin{itemize}
    \item Designed a scalable web-reports system from scratch.
  \end{itemize}}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

% \section{skills}
%   \vspace{-0.2cm}
% data science, programming computing at scale, machine learning
\vspace{-.5cm}
\section{publications}
  \vspace{-0.2cm}
 \begin{enumerate}
    \item \href{https://www.complexnetworks.org/program/}{R.Hartman, S.M. Seyednezhad, D. Pinheiro, \textbf{J. Faustino}, and R. Menezes. \jobtitle{Entropy in Network Community as an Indicator of Language Structure in Emoji Usage: {A} Twitter Study Across Various Thematic Datasets}. To Appear in Complex Networks. Dec. 2018 Cambridge UK.}
    \item \href{https://doi.org/10.1145/3106426.3106493}{R.Hartman, \textbf{J. Faustino}, D. Pinheiro and R. Menezes. \jobtitle{Assessing the suitability of network community detection to available meta-data using rank stability}. WI \'17, Aug 2017. Leipzig, DE.}
     \item \href{http://dx.doi.org/10.1007/978-1-4614-7163-9_78-1}{\textbf{J. Faustino}, R. Menezes, P. Divakamurthy. \jobtitle{Networks in Rural Sociology}.  Encyclopedia of Social Network Analysis and Mining. Springer 2017.} 
     \item \href{http://doi.computer.org/10.1109/BRICS-CCI-CBIC.2013.115}{ H. Barbosa-Filho, \textbf{J. Faustino}, R.R. Martins, R. Menezes. \jobtitle{Strategies, Political Position, and Electoral Performance of Brazilian Political Parties} BRICS-CCI \& CBIC. IEEE 2013. Recife, Brazil.}
 \end{enumerate}
%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{other qualifications}
\begin{entrylist}
%------------------------------------------------
\entry
{2017}
{High Performance Computing Summer School}
{University of California, San Diego}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2018}
{Graduate Mentor - REU National Science Foundation}
{Florida Institute of Technology}
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{awards}
\begin{entrylist}
%------------------------------------------------
\entry
{2018}
{Best Poster}
{COMPLENET \'18, Boston, MA}
{\href{https://complenet18.weebly.com/}{Best poster award in the conference out of 42 accepted posters in the session.}}
\entry
{2018}
{Computing Resources Grant}
{XSEDE - National Science Foundation}
{\href{https://portal.xsede.org/allocations/research}{Computing resources proposal submitted to XSEDE/NSF. Resources were used during the Machine Learning Research for Undergraduates Program in the Summer/2018.}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{interests}
%   \vspace{-0.2cm}

% \textbf{professional:} professional interest 1, professional interest 2 and professional interest 3. \textbf{personal:} personal interest 1, personal interest 2, personal interest 3 and personal interest 4.

%----------------------------------------------------------------------------------------

\end{document}